A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2019-03-07 referee_response.txt

Dear Anonymous Referee,

Thank you so much for your kind words and comments on the manuscript "A VLT/FORS2 Narrowband
Imaging Search for MgII Emission in z~0.70 Galaxies". Below is a list of your comments and
our edits according to these comments.

Comment:"In the last paragraph of Section 2.1 a little more information about the absorption lines would be helpful. 
The velocities are quoted as ~150-420 km/s -- is this measured from the centroids of the lines? 
As the authors know, the velocity of MgII can be significantly affected by infilling from emission, so a bit 
more detail on where these numbers come from and how to interpret them would be useful. 
It would also be helpful to note that the equivalent widths given here are in the rest frame, since 
they are discussed in the observed frame in most of the rest of the paper."

Reply: We expanded the last paragraph to include a refined description of the velocities being reported. We 
added the velocity reported for each galaxy in Table 1. Additionally, we discussed what type of model is being used
to measure the lines and how these mitigate the effect of infilling emission. We also note that the EW's mentioned
here are the rest-frame equivalent widths.

Comment: Please add a note to Table 1 explaining what tau_V is, since it isn't discussed until later in the paper
and it is a bit less obvious than the other quantities in the table.

Reply: We added a note to Table 1 which gives more insight to tau_V.

Comment:In the discussion of previous results in Section 6.1, I think providing some context from Henry et al 2018 would
be useful. Although this paper didn't present spatially extended emission, their results on which galaxies are 
likely to have strong MgII emission is relevant, in particular the finding that nebular emission is important as 
well as resonantly scattered continuum photons, and the finding that the strength of the emission may be set by the 
escape fraction of MgII photons rather than the intrinsic production.

Reply: Added a discussion of Henry et al 2016 and Guseva et al.(2019).

### 2019-03-07 for_submission/rvaught_2018.tex
03/06/2018

\documentclass[twocolumn]{aastex62}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{graphicx}
\usepackage{amsmath}

@@

The \textbf{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA. \textbf{Due to the photon scattering process described in Section \ref{sec:intro}, it is possible that scattered emission can fill in the deepest parts of the absorption line near systemic velocity and shift the trough of the line blueward. To mitigate the effects of any scattered emission, \cite{Rubin_2014} implement a two velocity component ``flow" model in tandem with a single ``fixed-velocity", with respect to the central wavelength of \ion{Mg}{2}, model to quantify the absorption line kinematics. The qualitative conetext of this scattering process, as it pertains to galactic winds, can be improved via higher resolution spectrum and radiative transfer analysis \cite{Prochaska_2011}}. Modeling of the galaxy broad-band spectral energy distributions (SEDs) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$. The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014}, are listed in Table \ref{tab:prop}.

@@

\begin{deluxetable*}{c c c c D D c D}
\tablecaption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
\tablehead{\colhead{Object} & \colhead{R.A.} & \colhead{Dec} & \colhead{$z$} & \multicolumn2c{SFR} & \multicolumn2c{$\log{(M)}$} & \colhead{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$} \\ 
\colhead {} & \colhead {} & \colhead {} & \colhead{} & \multicolumn2c{($M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(\AA)} & \multicolumn2c{}}
\decimals
\startdata
J033225.26-274524.0 (J.26)     & 03:32:25.26 & -27:45:23.9  &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   & \ $7.5\pm 0.4$   &  $1.227_{-0.20}^{+1.54}$ \\ 
J033231.36-274725.0 (J.36)     & 03:32:31.35 & -27:47:24.9  &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ & \ $5.8 \pm 0.5$   & $1.377_{-0.23}^{+0.60}$ \\
J033230.03-274347.3 (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   & $12.8 \pm 1.7$ & $0.297_{-0.0}^{+0.0}$ \\
J033229.64-274242.6 (J.64)     & 03:32:29.64 & -27:42:42.5  &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ & $13.2 \pm 0.3$ & $3.897_{-0.93}^{+1.15}$ \\
J033230.57-274518.2 (J.57)     & 03:32:30.56 & -27:45:18.2  &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ & \ $6.1 \pm 0.4$   & $1.262_{-0.40}^{+1.23}$ \\
\enddata
\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ i.e. \textbf{dust opacity of the galaxy}, values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
\end{deluxetable*}

\begin{deluxetable}{c c c c c c}
\tablecaption{Filter properties  and exposure times of the VLT/FORS2 observations. The widths of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curves over the total wavelength range of each filter. 
%These values differ slightly from those reported by the European Southern Observatory.
 \label{tab:filters}}
\tablehead{\colhead {Filter (Line)} & \colhead {$\lambda_{\rm{eff}}$\tablenotemark{a}} & \colhead {$\Delta\lambda$\tablenotemark{b}} & \colhead {N\tablenotemark{c}} & \colhead{$T$\tablenotemark{d}} & \colhead{$S$\tablenotemark{e}} \\
\colhead {} & \colhead{(\AA)} & \colhead{(\AA)} & \colhead{} & \colhead{(sec)} & \colhead{}}
\startdata
HeII+47 (\ion{Mg}{2})         & 4675.21  & 50.11 & 38  & 35,959 & 2.45 \\
HeII/3000+48 (Cont.) & 4722.46  & 44.82 & 38  & 36,937 & 2.40  \\
\enddata
\tablenotetext{a}{$ \lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.}
\tablenotetext{b}{The effective width of the filter.}
\tablenotetext{c}{Total number of images.}
\tablenotetext{d}{Total exposure time.}
\tablenotetext{e}{S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$.}
\end{deluxetable}\ 
%\\

@@

\subsection{Strength of \ion{Mg}{2} emission and Correlation with Galaxy Properties }
\textbf{The middle panel of Figure \ref{fig:all_limits} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies. A similar trend was observed by both \cite{Erb2012} and \cite{Feltre2018} in their examination of the total \ion{Mg}{2} emission strength vs. galaxy $M_*$. IN addition to the observed trend that emission strength may be correlated with galaxy mass, a recent study by \cite{Henry2018} detected significant \ion{Mg}{2} emission, characterized with escape fractions between $0-0.9$, in a sample of $z \sim 0.2-0.3$ Green Pea galaxies.   Finally, the right panel of Figure \ref{fig:all_limits} shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR. If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFRs, exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material}

@@

\newpage
\bibliography{references2017}

\end{document}

>>>>

%\documentclass[twocolumn]{aastex62}
\documentclass[trackchanges,twocolumn]{aastex62}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{graphicx}
\usepackage{amsmath}

@@

The \added{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2} with \added{maximum outflow} velocities, $\Delta v_{\rm max}$ $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA. \added{The reported maximum outflow velocities, see Table \ref{tab:prop}, are the result of fitting a two-velocity component model to the absorption line profile. The two component model assumes that there is a systemic velocity and ``flow" velocity that both contribute to the overall line profile. The maximum outflow velocity is the velocity of the flow, $v_{\rm flow}$ minus a fitted doppler parameter, $b_{D,\rm flow}/\sqrt{2}$. The use of the two component model is helpful to mitigate the effects of scattered emission filling up the absorption line which in turn pushes the trough of the line blueward. It is assumed that the resonant emission will reduce the systemic velocity, leaving the flow velocity to characterize the outflow. The qualitative context of this scattering process, as it pertains to galactic winds, can be improved via higher resolution spectrum and radiative transfer analysis \cite{Prochaska_2011}}. Modeling of the galaxy broad-band spectral energy distributions (SEDs) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$. The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014}, are listed in Table \ref{tab:prop}.

@@

%\begin{deluxetable*}{c c c c D D c D}
%\tablecaption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
%determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
%\tablehead{\colhead{Object} & \colhead{R.A.} & \colhead{Dec} & \colhead{$z$} & \multicolumn2c{SFR} & \multicolumn2c{$\log{(M)}$} & \colhead{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$} \\ 
%\colhead {} & \colhead {} & \colhead {} & \colhead{} & \multicolumn2c{($M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(\AA)} & \multicolumn2c{}}
%\decimals
%\startdata
%J033225.26-274524.0 (J.26)     & 03:32:25.26 & -27:45:23.9  &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   & \ $7.5\pm 0.4$   &  $1.227_{-0.20}^{+1.54}$ \\ 
%J033231.36-274725.0 (J.36)     & 03:32:31.35 & -27:47:24.9  &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ & \ $5.8 \pm 0.5$   & $1.377_{-0.23}^{+0.60}$ \\
%J033230.03-274347.3 (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   & $12.8 \pm 1.7$ & $0.297_{-0.0}^{+0.0}$ \\
%J033229.64-274242.6 (J.64)     & 03:32:29.64 & -27:42:42.5  &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ & $13.2 \pm 0.3$ & $3.897_{-0.93}^{+1.15}$ \\
%J033230.57-274518.2 (J.57)     & 03:32:30.56 & -27:45:18.2  &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ & \ $6.1 \pm 0.4$   & $1.262_{-0.40}^{+1.23}$ \\
%\enddata
%\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ i.e. \textbf{dust opacity of the galaxy}, values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
%\end{deluxetable*}

\begin{deluxetable*}{c c D D D c D}
\tablecaption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
\tablehead{\colhead{Object\tablenotemark{a}} &  \colhead{$z$} & \multicolumn2c{SFR} & \multicolumn2c{$\log{(M)}$} &\colhead{$\Delta v_{\rm max}$\tablenotemark{b}} &\multicolumn2c{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$\tablenotemark{c}} \\ 
\colhead {} & \colhead{} & \multicolumn2c{($M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(km s$^{-1}$)} & \multicolumn2c{(\AA)} & \multicolumn2c{}}
\decimals
\startdata
J033225.26-274524.0 (J.26)     &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   &   $-187_{-16}^{+12}$ & \ $7.5\pm 0.4$   &  $1.227_{-0.20}^{+1.54}$ \\ 
J033231.36-274725.0 (J.36)     &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ &   $-168_{-126}^{+33}$ & \ $5.8 \pm 0.5$   & $1.377_{-0.23}^{+0.60}$ \\
J033230.03-274347.3 (J.03)     &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   &   $-400_{-64}^{+132}$ & $12.8 \pm 1.7$ & $0.297_{-0.0}^{+0.0}$ \\
J033229.64-274242.6 (J.64)     &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &   $-378_{-12}^{+12}$ & $13.2 \pm 0.3$ & $3.897_{-0.93}^{+1.15}$ \\
J033230.57-274518.2 (J.57)     &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ &   $-266_{-38}^{+44}$ & \ $6.1 \pm 0.4$   & $1.262_{-0.40}^{+1.23}$ \\
\enddata
\tablenotetext{a}{\added{Galaxy ID's are named according to the object R.A and DEC. position.}}
\tablenotetext{b}{\added{Maximum outflow velocity, $\Delta v_{\rm max} \approx v_{\rm flow}- b_{D,\rm flow}/\sqrt{2}$ where $b_{D,\rm flow}$ is the Doppler parameter or velocity width of the absorption.}}
\tablenotetext{c}{\added{Total V-band optical depth.}} 
\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
\end{deluxetable*}

\begin{deluxetable}{c c c c c c}
\tablecaption{Filter properties  and exposure times of the VLT/FORS2 observations. The widths of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curves over the total wavelength range of each filter. 
%These values differ slightly from those reported by the European Southern Observatory.
 \label{tab:filters}}
\tablehead{\colhead {Filter (Line)} & \colhead {$\lambda_{\rm{eff}}$\tablenotemark{a}} & \colhead {$\Delta\lambda$\tablenotemark{b}} & \colhead {N\tablenotemark{c}} & \colhead{$T$\tablenotemark{d}} & \colhead{$S$\tablenotemark{e}} \\
\colhead {} & \colhead{(\AA)} & \colhead{(\AA)} & \colhead{} & \colhead{(sec)} & \colhead{}}
\startdata
HeII+47 (\ion{Mg}{2})         & 4675.21  & 50.11 & 38  & 35,959 & 2.45 \\
HeII/3000+48 (Cont.) & 4722.46  & 44.82 & 38  & 36,937 & 2.40  \\
\enddata
\tablenotetext{a}{$ \lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.}
\tablenotetext{b}{The effective width of the filter.}
\tablenotetext{c}{Total number of images.}
\tablenotetext{d}{Total exposure time.}
\tablenotetext{e}{S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$.}
\end{deluxetable}\

@@

\subsection{Strength of \ion{Mg}{2} emission and Correlation with Galaxy Properties }
\added{The middle panel of Figure \ref{fig:all_limits} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies. A similar trend was observed by both \cite{Erb2012} and \cite{Feltre2018} in their examination of the total \ion{Mg}{2} emission strength vs. galaxy $M_*$. In addition to the observed trend that emission strength may be correlated with galaxy mass, recent studies by \cite{Henry2018} and \cite{Guseva2019} show significant contribution from nebular emission to the total \ion{Mg}{2} emission strength. In \cite{Henry2018} report strong \ion{Mg}{2} emission, characterized with escape fractions between $0-0.9$, in a sample of $z \sim 0.2-0.3$ Green Pea galaxies. Photoionization modeling of the observed strength of emission suggests that in addition to scattering of continuum photons, HII regions may also produce a non-negligible contribution to observed \ion{Mg}{2} emission, with the strength set b the escape fraction. In \cite{Guseva2019}, the authors find that low metallicity \ion{Mg}{2} emitters from \cite{Feltre2018} and \cite{Finley2017} have high H$\beta$ EW's, confirming that \ion{Mg}{2} emission has nebular origin. However, our sample of galaxies are comparitavely more massive and thus richer in metal than the galaxies that are known to contain significant nebular emission. The total contribution from nebular \ion{Mg}{2} to the total \ion{Mg}{2} emission remains to be determined for more massive and metal rich galaxies.}

Finally, the right panel of Figure \ref{fig:all_limits} shows that the galaxy with detected extended \ion{Mg}{2} also has the highest specific SFR. If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFRs, exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.

@@

\newpage
\bibliography{references2017}
\listofchanges
\end{document}
